### 2022-08-30 paper/icse23/intro.tex

\Nlp (NLP) applications are growing exponentially.  As a result,
trustworthiness in the quality of NLP applications has become critical
for its practical use in the real world.  Therefore, quality assurance
of NLP applications is an essential process in the software
development processes.  Researchers aim to improve the current
practices of testing NLP models from three perspectives: (i)
\emph{Test input generation}, (ii) \emph{Automated test oracle}, and
(iii) \emph{Meaningful quality metrics}.

\noindent \textbf{Test input generation.} Currently, most testing of
an NLP model reuses existing large textual corpus as the testing
dataset to evaluate the model. This practice will often overestimates
the model performances from the \ho
set~\cite{patel2018mlevalforsoftware, recht2019imagenetbias,
  marcoACL2020checklist}.  The overestimation comes from the
discrepancy between the distribution of the used dataset and the
actual data distribution in real world. Oftentimes, the \ho dataset is
not representative and is likely to introduce specific biases, leading
to the decreased robustness of NLP models. In this regard, prior works
have proposed techniques for testing the robustness of NLP models by
crafting adversarial examples and attacking a model with them
intentionally \cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial}.

\noindent \textbf{Automated test oracle.} The current testing practice
requires manual work for labelling the test oracles of the \ho
data. The manual work is costly in terms of time consumption and its
impact on market price. Therefore, it necessitates automated test
oracle generation for improving the testing process of NLP models.
% validity of the automation is ensured by the
% correctness of test oracle.
However, automatically generated test oracles may not always be
feasible; predicting the correct test oracles remains one of main
challenges. Along with this, software metamorphic testing approach has
been introduced~\cite{segura2016metamorphictest} to alleviate the test
oracle discrepancy between expected and observed test oracles.
% \TODO{Describe and Add citations to metamorphic testing techniques
%   here}\jl{done.}

%% \sw{Not sure what overestimate means here}
%  In addition, the inconsistency between test input and
% its oracle causes biases. Such biases increase the discrepancy of
% distribution between the dataset and real-world data.
\noindent \textbf{Meaningful quality metrics.}  Traditionally, the
quality of NLP models are represented by numbers in quality
metrics. Especially, accuracy (i.e., the fraction of outputs that the
model correctly predicts) is the most widely used metric for assessing
the quality of classification models.  Generally, higher accuracy
number suggests better quality of a model.  However, all NLP models
have their strength and weakness and forcing aggregation statistics
into a single number makes the users difficult to assess the
capabilities of NLP models.  Not to mention localizing and fixing the
bugs found from the \ho set (i.e., testing dataset, as opposed to
training dataset). Therefore, this forced aggregation method not only
fails to validate the linguistic capability of the model, but it also
makes the localization of the causes of the inaccuracy more
costly~\cite{wu2019errudite}.
% Therefore behavioral testing
% approach provides the better ability to examine the inaccuracy and
% find the bugs in the model.
To address this limitation,
% several approaches have been proposed to
% evaluate different aspects of the NLP models, such as , model coverage
% \cite{rottger2020hatecheck}, and fairness
% \cite{prabhakaran2019fairness,rottger2020hatecheck}. In addition, For example, Testing model coverage
% only shows model behaviors, but not the model performance on existing
% testing set. The fairness and robustness testing only focus on only
% one model capability resulting in its limited comprehensiveness. In
% addition,
Ribeiro~\etal introduced \Cklst, a behavioral testing framework for
evaluating NLP model on multiple linguistic
capabilities~\cite{marcoACL2020checklist}. \Cklst defines
task-relevant linguistic capabilities and generates test cases for
each \lc.

However, none of the above approaches satisfy all three requirements
at the same time. First, adversarial testing approaches merely focus
on evaluating model robustness. They measure how sensitive the models
are to input perturbations while do not evaluate linguistic
functionalities.  Second, the metamorphic testing approach is required
to understand the characteristics of metamorphic relations between
inputs and outputs. However, finding these remains one of the most
challenging problem in metamorphic
testing~\cite{segura2016metamorphictest}. Along with this, such
relation in textual data in NLP domain has not been evaluated despite
its importance.  Third, \Cklst relies on manually generated input
templates, which need to be preset before test input
generation. Consequently, \Cklst templates are distributed in a
limited range of their structures. This restricts \Cklst's ability to
comprehensively test the linguistic capabilities.

Despite \Cklst's limitations, assessing the quality of NLP models
through the linguistic capabilities is a promising direction. Each \lc
explains the functionality of the input and output behavior for the
NLP model under test. Typically, it describes certain type of inputs
and outputs observed in real world for the target NLP task ranging
from simple to complicated behaviors, so the model developers can
better understand the capabilities and potential issues of the NLP
models. For example, a linguistic capability of ``Negated neutral
should still be neutral'' measures how accurately the \sa model
understands the negative neutral input as an neutral sentiment
\cite{marcoACL2020checklist}.  Therefore, it requires the \sa model to
output neutral sentiment on the negated neutral input.  Such
methodology of evaluation on the specified functionalities avoids the
overestimation of the model performance as it equivalently measures
the model performance on each functionality.
% ,and the separate model performance
% explain distribution of the performance over the linguistic capabilities
In the end, testing through linguistic capabilities provides not only
the overall model performance, but also the malfunction facets of the
model.

To satisfy all three requirements mentioned above, we present \tool,
an automated NLP model evaluation method for comprehensive behavioral
testing of NLP models on \sa task.  There are three main challenges
that \tool overcomes to satisfy all three aforementioned requirements.
\begin{description}
\item[{\bf C1}] The test suite should cover diverse syntactic structures;
\item[{\bf C2}] Each test case should be categorized into a \lc;
\item[{\bf C3}] The label of each test case should be automatically
  and accurately defined.
\end{description}

\noindent \textbf{C1.} The first challenge comes with the second and
third challenges of maintaining the label and linguistic capability of
the test sentence while making the syntactic structure of the sentence
more diverse. In addition, text have a higher order of structures and
structures are obscured by word usage~\cite{}. To address the
challenge, \tool establishes specifications for evaluating a
linguistic capability and searches suitable sentences that satisfy the
specification from existing public dataset. In this process, \tool
generates new inputs by mutating the searched sentences, used as seed
inputs. \tool expands seed input grammar structures and determines its
available \pos to maintain structural naturalness.

@@

\noindent \textbf{C2.} Suitability of test sentences for evaluating
NLP model on a \lc is obtained from its high relevancy to the
\lc. Relevancy between a test sentence and its \lc is challenging to
be maintained during the transformation and expansion of the test
sentence.  This is because the \lc is defined on a specific mixture of
syntaxe and semantics of the sentence, and there exists no automatic
way to check the consistency between each sentence with the semantics
specified in corresponding \lc due to the inherent ambiguity of
natural language sentences. To address the difficulty, \tool
implements search rules and the transformation templates of \lcs. In
addition, anlyzing parse tree of seed sentence is used for its
expansion identification.
%% \tool adopts behavioral model testing method by
%% introducing multiple behaviors from \lcs on \sa tasks and generating
%% inputs relevant to each \lc. Each test case provides not only
%% correctness of model prediction on it, but \lc on the test case also
%% gives information about classification on the model
%% performance. Therefore assigning appropriate \lc for each test case
%% alleviates overestimation of model testing results.

\noindent \textbf{C3.} Last challenge is on automated test oracle.
For NLP tasks, test oracle is determined by understanding meaning from
texts. This requires domain knowledge for different NLP tasks
% Therefore, generation of test case ought to ensure the
%correctness of its oracle allocation.
In this work, as a first step, we consider \sa as the NLP task for the
models under test. \tool obtain the appropriateness of test oracle by
implementing domain-specific knowledge on word sentiment dataset and
word suggestion model pre-trained on large corpus for validation of
generated sentence and its oracle.

We demonstrate its generality and utility as a NLP model evaluation
tool by evaluating well-known \sa models: \Bert~\cite{devlin2019bert},
\Roberta~\cite{liu2019roberta} and \Dbert~\cite{sanh2019distilbert}.
We show that ...

>>>>

\Nlp (NLP) applications are growing exponentially.  As a result,
trustworthiness in the quality of NLP applications has become critical
for its practical use in the real world.  Therefore, quality assurance
of NLP applications is essential in the software
development process.  
Researchers aim to improve the current practices of testing NLP models
from three perspectives: (i) \emph{test input generation}, (ii)
\emph{automated test oracle}, and (iii) \emph{meaningful quality
  metrics}.

\noindent \textbf{Test input generation.} Currently, most testing of
an NLP model uses existing, large textual corpus as the testing
dataset to evaluate the model. This practice often overestimates
the model performances from the \ho
dataset~\cite{patel2018mlevalforsoftware, recht2019imagenetbias,
  marcoACL2020checklist}.  The overestimation comes from the
discrepancy between the distribution of the used dataset and the actual data
distribution in real world. Oftentimes, the \ho dataset is not
representative and is likely to introduce specific biases, leading to the
decreased robustness of NLP models. In this regard, prior works
have proposed techniques for testing the robustness of NLP models by crafting
adversarial examples and attacking a model with them intentionally (i.e., adversarial testing)
\cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial}.

\noindent \textbf{Automated test oracle.} The current testing practice
requires manual efforts to label the test oracles of the \ho
data. The manual work is costly in terms of time consumption and its
impact on the market price. Therefore, it necessitates automated test
oracle generation for improving the testing process of NLP
models. 
% validity of the automation is ensured by the
% correctness of test oracle.
However, automatically generating test oracles may not always
be feasible; predicting the correct test oracles remains one of main
challenges. Along with this, motivated by software metamorphic testing 
approach~\cite{segura2016metamorphictest}, we address the challenge by specifying linguistic rules determined by input-output relations, and we only accept validated test oracles by the rules. 
% \TODO{Describe and Add citations to metamorphic testing techniques
%   here}\jl{done.}

%% \sw{Not sure what overestimate means here}
%  In addition, the inconsistency between test input and
% its oracle causes biases. Such biases increase the discrepancy of
% distribution between the dataset and real-world data.
\noindent \textbf{Meaningful quality metrics.}  
Traditionally, the quality of NLP models are
represented by numbers in quality metrics. Especially, accuracy (i.e., the fraction of outputs that the
model correctly predicts) is the most widely used metric for assessing
the quality of classification models. 
Generally, higher accuracy number suggests better quality of a model.
However, all NLP models have their strengths and weaknesses, and 
forcing aggregation statistics into a single number (i.e., accuracy) makes it difficult for the users to assess the capabilities of NLP models.  Not to
mention localizing and fixing the bugs found from the \ho
set (i.e., testing dataset, as opposed to training dataset). Therefore, this forced aggregation method not only fails to
validate the linguistic capability of the model, but it also makes the localization of the
causes of the inaccuracy more costly~\cite{wu2019errudite}.
% Therefore behavioral testing
% approach provides the better ability to examine the inaccuracy and
% find the bugs in the model.
To address this limitation,
% several approaches have been proposed to
% evaluate different aspects of the NLP models, such as , model coverage
% \cite{rottger2020hatecheck}, and fairness
% \cite{prabhakaran2019fairness,rottger2020hatecheck}. In addition, For example, Testing model coverage
% only shows model behaviors, but not the model performance on existing
% testing set. The fairness and robustness testing only focus on only
% one model capability resulting in its limited comprehensiveness. In
% addition,
Ribeiro~\etal introduced \Cklst, a behavioral testing framework for
evaluating NLP model on multiple linguistic
capabilities~\cite{marcoACL2020checklist}. \Cklst defines
task-relevant linguistic capabilities and generates test cases for
each \lc.

However, none of the above approaches satisfy all three requirements
at the same time. First, the adversarial testing approaches merely
focus on evaluating model robustness. They measure how sensitive the models
are to input perturbations while do not
evaluate linguistic functionalities.
Second, the metamorphic testing approach requires understanding the characteristics of metamorphic relations between inputs
and outputs. However, finding these remains one of the most challenging
problems~\cite{segura2016metamorphictest}. In addition, metamorphic
relation in textual data in the NLP domain has not been explored despite
its importance.
Third, \Cklst relies on manually generated input templates,
which need to be preset before test input generation. Consequently,
\Cklst templates are distributed in a limited range of their
structures. This restricts \Cklst's ability to comprehensively test
the linguistic capabilities.

Despite \Cklst's limitations, assessing the quality of NLP models
through the linguistic capabilities is a promising direction. Each \lc
explains the functionality of the input and output behavior for the
NLP model under test. Typically, it describes certain type of inputs
and outputs observed in real world for the target NLP task, ranging
from simple to complicated behaviors. Testing the linguistic capabilities allows the model developers to better understand the capabilities and potential issues of the NLP
models. For example, a linguistic capability of ``Negated neutral
should still be neutral'' measures how accurately the \sa model
understands that the negated neutral input has neutral sentiment
\cite{marcoACL2020checklist}, requiring the \sa model to
output neutral sentiment on the negated neutral inputs.  Such evaluation
methodology on the specified functionalities avoids the
overestimation of the model performance as it measures
the model performance on each functionality.
% ,and the separate model performance
% explain distribution of the performance over the linguistic capabilities
In the end, testing through linguistic capabilities provides not only
the overall model performance, but also the malfunction facets of the
model.

To satisfy all three requirements mentioned above, we present \tool,
an automated evaluation method for comprehensive behavioral
testing of NLP models on \sa task.  There are three main challenges
that \tool overcomes to satisfy all three aforementioned requirements.
\begin{description}
\item[{\bf C1}] The test suite should cover diverse syntactic structures;
\item[{\bf C2}] Each test case should be automatically categorized into a \lc;
\item[{\bf C3}] The label of each test case should be automatically
  and accurately defined.
\end{description}

\noindent \textbf{C1.} The first challenge comes with the second and third challenges of maintaining the linguistic capability and label of the test sentence while making the syntactic structure of the sentence diverse. 
To address this challenge, \tool establishes specifications for evaluating
a linguistic capability and searches suitable sentences that satisfy
the specification from existing public dataset. In this process, \tool
generates new inputs by mutating the searched sentences, used as seed
inputs. \tool expands the grammar structure of a seed input and determines its
available \pos to maintain structural naturalness.

@@

\noindent \textbf{C2.} Suitability of test sentences for evaluating NLP
model on a \lc is determined by its relevancy to the
\lc. Relevancy between a test sentence and its \lc is challenging to be maintained when transforming and expanding the test sentence.
This is because the \lc is defined on a specific 
mixture of syntax and semantics of the sentence, and there exists no automatic way to check the consistency of each sentence with the semantics specified in the corresponding \lc due to the inherent ambiguity of natural language sentences. To address this difficulty, \tool implements search rules
and the transformation templates of \lcs. In addition, it analyzes the parse
tree of the seed sentence to identify possible expansion.
%% \tool adopts behavioral model testing method by
%% introducing multiple behaviors from \lcs on \sa tasks and generating
%% inputs relevant to each \lc. Each test case provides not only
%% correctness of model prediction on it, but \lc on the test case also
%% gives information about classification on the model
%% performance. Therefore assigning appropriate \lc for each test case
%% alleviates overestimation of model testing results.

\noindent \textbf{C3.} Last challenge is on automated test oracle.  For NLP tasks, test oracle is
determined by understanding the meaning of texts. This requires domain knowledge of different NLP tasks.
% Therefore, generation of test case ought to ensure the
%correctness of its oracle allocation.
In this work, as a first step, we consider \sa as the NLP task for the models under test. \tool obtains the
appropriate test oracle by implementing domain-specific
knowledge on the word sentiment dataset and word suggestion model for validation of generated sentence and its oracle.

We demonstrate the generality of \tool and its utility as a NLP model evaluation
tool by evaluating three well-known \sa models: \Bert~\cite{devlin2019bert},
\Roberta~\cite{liu2019roberta} and \Dbert~\cite{sanh2019distilbert}.

\vspace{2pt}
\noindent
We made the following contributions in this work:

\begin{itemize}[topsep=3pt,itemsep=3pt,partopsep=0ex,parsep=0ex,leftmargin=*]
\item We design and implement an automated testing tool, \tool, and compared it with \Cklst. We find that the test cases generated by \tool achieves higher coverage than \Cklst when used for testing sentiment analysis models.
%
\item We perform a manual study to
measure the correctness of the sentiment labels and their \lcs produced by \tool. We find that \tool generates test cases that consistently label their sentiment correctly as human understanding.
%
\item We analyze the root causes of the misclassification in the sentiment analysis models, guided by \tool testing result. We find that seed and expanded test cases, produced by \tool, are usefulness of \tool for understanding bugs in the models.
\end{itemize}

% \sw{results are missing}

% \sw{Do we want to explicitly list contributions?}
